Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-17 cordillera-cycle.tex
Regroup GRIP and EPICA deglaciation snapshots.

@@

% fig:deglacshots-grip
\begin{figure*}
  \includegraphics{deglacshots-grip}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial ice volume maximum (19.1\,kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-grip}
\end{figure*}

% fig:deglacshots-epica
\begin{figure*}
  \includegraphics{deglacshots-epica}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) from the EPICA simulation,
           corresponding to the last glacial ice volume maximum (17.3\,kyr) and
           the last deglaciation.}
  \label{fig:deglacshots-epica}
\end{figure*}

>>>>

% fig:deglacshots
\begin{figure*}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) during the last deglaciation
           from the GRIP (top panels) and EPICA (bottom panels) simulations.}
  \label{fig:deglacshots-grip}
\end{figure*}

@@
